Self-test prime dimensional EPR pairs with constant alphabet

### 2019-03-31 Draft/draft.tex
Honghao: reorganized the Prelim section: put linear system game and nonlocal game part together and remove definitions of solution group and operator solution

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{EPR^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tX}{\tilde{X}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tU}{\tilde{U}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}

@@

@@

In order to accomplish our goal, we introduce new techniques for self-testing.
First of all, we use a different variant of the weighted CHSH inequality to enforce the eigenvalue of
some unknown operator which is the product of two binary observables used in the weighted CHSH test.
\carl{I think this game might have been defined in APM12, and if so we need to cite it.}
The variant of the CHSH inequality that we use is not used in the self-testing literature before.
Secondly, we give a new way to decompose unitaries of arbitrary order into binary observables which maintains
certain commutation relations. Such decomposition is different from what Slofstra used in his work \cite{slofstra2017}.
\carl{Our work is heavily based on \cite{slofstra2017}, and we need to make that clearer.}
Intuitively, such decomposition can be seen as the inverse of the Jordan's lemma decomposition.
The third contribution is that we prove self-testing without using anti-commutation relations between Pauli operators, 
which is the core idea in all the previous self-testing results.
\carl{Are we sure about that ("all")?}
Instead, we find a new pair of operators that can generate the ring of matrices over complex numbers.

@@

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
We use $[n]$ to denote the set $\{0,1 \dots n-1\}$ and $[n]+1$ for the set $\{1,2 \dots n\}$.
%We denote the group commutator of $A$ and $B$, i.e. $ABA^{-1}B^{-1}$, by $[A,B]$.

We use some basic number theory in our work. A primitive root of a prime number
$d$ is an integer $r$ such that $r \pmod{d}$ has multiplicative order $d-1$. Equivalently,
$r$ is the generator of the multiplicative group of integers modulo $d$, $\Zd$ where
$\Zd = \{1,2\dots d-1\}$. \textcolor{red}{When the prime number $d$ has multiple primitive roots,
we always work with the smallest one.}
\carl{I'm not clear on what that last sentence means.  You just defined what a primitive root
is --- are you changing the definition now?}

The EPR pair of local dimension $d-1$ for some prime $d$ is denoted by
\begin{align}
\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{i = 0}^{d-2} \ket{ii}.
\end{align}
The superscript $(d-1)$ stresses the local dimension and we follow this convention through this paper.

We self-test $\ket{\EPR{d-1}}$ by verify that Alice and Bob has operators
\begin{align}
	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/r}{k},
\end{align}
where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity,
and $r$ is the primitive root of $d$.  \carl{That sentence is jumping ahead --- you should just stick to
definitions and notation for now.}
Through out this paper, any operation on the label of the eigenvector $\ket{k}$ is taken modulo $d$,
unless otherwise specified, for example, the $k/r$ above.

\textbf{The weighted CHSH inequality \cite{acin2012}.}
The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
In the CHSH scenario, Alice and Bob has binary observables $A_x,B_y$ for $x,y = 1,2$ 
on Hilbert space $\calH_A$ and $\calH_B$ respectively.  \carl{It needs to be clearer who Alice and Bob
are --- perhaps you should put this subsection after the ``Nonlocal games'' subsection.}
A binary observable is a Hermitian matrix whose only eigenvalues are either $+1$ or $-1$.
The weighted CHSH inequality is given by 
\begin{align}
	\label{eq:chsh_op}
	\I_\alpha = \alpha\ip{A_1B_1}+\alpha\ip{A_1B_2} + \ip{A_2B_1} - \ip{A_2B_2}\leq 2\alpha,
\end{align}
where $\ip{A_xB_y}$ is the expectation value of of the observables.  \carl{Same here -- it's not clear enough
what this means until the reader has seen the ``Nonlocal games'' subsection.}
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
the weighted CHSH inequality.
However, If they share entangled state $\ket{\psi}$, the maximal violation is 
\begin{align}
\label{eq:chsh_max}
 \I_\alpha \leq 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy for $\I_\alpha$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
	consists of the joint state $\ket{\EPR{2}}$ and observables $A_1 = \pauliz$, $A_2 = \paulix$,
	$B_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
\carl{Just to be complete, you should say what $\pauliz$ and $\paulix$ denote.}
An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
measurements up to isometry, 
which is a phenomenon referred as a self-test. We give formal statement of this self-testing result in \cref{sec:chsh}.

@@

A quantum strategy of a game $G$ consists of projective measurements $\{\{A_x^a\}_a\}$ on Alice's side, 
$\{\{B_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where a projective measurement $P$ satisfies
the condition that $P^2 = P = P\ct$.  \carl{You need to put explicit labels on the quantum systems used by
Alice and Bob.  (Later on you seem to use ``$A$'' and ``$B$'' to refer to those systems, but those are also
the same letters you use for Alice's and Bob's measurements.  That's confusing.)}
Then Alice and Bob's quantum strategy produces the correlation
\begin{align}
	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
where $(A_x^a)^2 = A_x^a = (A_x^a)^\dagger$ and $(B_y^b)^2 = B_y^b = (B_y^b)^\dagger$.
%Note that we may use the term behaviour and correlation interchangeably.
%The value of a strategy is given by
%\begin{align}
%	\omega(G,p)  = \sum_{a,b,x,y} \pi(x,y) \pr{ab}{xy} V(a,b,x,y).
%\end{align}

The main contribution of our work is the construction of a correlation, which is the combination of 
the optimal correlation of a linear system game with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
and the optimal correlation to violate the weighted CHSH inequality.  \carl{The reader does not 
know yet what a linear system game is, so this comment is more confusing than helpful.}
The special property of the correlation is that it can self-test $\ket{\EPR{d-1}}$ for arbitrary $d$ with certain 
primitive root. 
In the next part, we introduce the definition of self-testing, the definition of linear system game, 
and its operator solution, 
following definitions given in Ref.~\cite{coladan2017, slofstra2017}.

\carl{Before the next definition, you should define what a ``correlation'' is.}
\begin{definition}[Self-testing]
	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
	such that 	
	\begin{align*}
		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
	\end{align*}
\end{definition}
\begin{definition}[Linear system game]
 Let $Hx = c$ be an $m \times n$ system of linear equations over $\Z_2$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2 = \{0,1\}$ and 
 $c$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = [m]+1$ and replies with $a \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = [n]+1$ and replies with an assignment $b \in \calB = \Z_2$. The winning condition is 
 that Alice's assignment to the variables should satisfy equation $i$ and Alice's $j$-th assignment $a(j)$ should match $b$.
 Formally, the winning condition is 
 \begin{align*}
 	a(j) &= b && \text{(Consistency)} \\
	\sum_{k= 1}^n H(i,k) a(k) &\equiv c(i) \pmod 2. &&\text{(Constraint satisfaction)},
 \end{align*}
 for all $(i,j) \in \calX \times \calY$. 
\end{definition}
The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.  \carl{Make this clear in the definition itself.}
We focus on quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy for the linear system game $(Hx = c)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{c(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement, and
vice versa.  \carl{This is not entirely true.  A ``quantum strategy presented in terms of projective measurement'' allows
Alice to give answers that violate the ``Constraint satisfaction'' condition, while a ``quantum strategy presented 
in terms of binary observables'' does not.}

It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
operator solution in the following sense.  \carl{There's a missing reference here?}
\begin{definition}[Operator solution of a linear system]
\label{def:op_sol}
	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of bounded Hermitian 
	operators $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that \carl{(What does the word ``bounded'' mean here?  It might
	be best to just state the definition for finite dimensions only.)}
	\begin{enumerate}
		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
		\item for all $1 \leq i \leq m$,
		\begin{align*}
			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
		\end{align*}
	\end{enumerate}
	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
	solution in which the Hilbert space is finite-dimensional.
\end{definition}
Perfect quantum strategies can be extracted from operator solutions and vice versa.
Another angle to look at the linear system game ($Hx = c$) is a finitely presented group
over $\Z_2$, which is called the solution group.
\begin{definition}[Solution group of a linear system game]
	\label{def:presentation}
	Let $Hx = c$ be an $m \times n$  linear system. The solution group of this system
	is the group
	\begin{align*}
		\Gamma(H,c) := \ip{
		x_1,\dots x_n, J: &J^2 = x_i^2 = e \text{ for all }1 \leq i \leq n, \\
				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
				} .
	\end{align*}
\end{definition}
\carl{Don't you also need a commutativity condition for $J$ with $\{ x_i \}$?}
For concepts about group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
Combining \cref{def:op_sol} and \cref{def:presentation}, we know that an operator solution associated to $Hx =c$ is 
a finite-dimensional representation of $\Gamma(H,c)$ that maps $J$ to $-\1$.

>>>>

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{\Sigma^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tX}{\tilde{X}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tU}{\tilde{U}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}

@@

% Square root of epsilon
\newcommand{\ep}{\epsilon}
\newcommand{\se}{\sqrt{\epsilon}}
\newcommand{\qe}{\epsilon^{1/4}}
\newcommand{\sd}{\sqrt{d}}
\newcommand{\sr}{\sqrt{r}}
\newcommand{\qd}{d^{1/4}}

% Approximately equatli
\newcommand{\appd}[1]{\simeq_{#1}}

@@

In order to accomplish our goal, we introduce new techniques for self-testing.
First of all, we use a different variant of the weighted CHSH inequality, \hf{which was first introduced in \cite{acin2012}}, to enforce the eigenvalue of
some unknown operator which is the product of two binary observables used in the weighted CHSH test.
The variant of the CHSH inequality that we use is not used in the self-testing literature before.
Secondly, we give a new way to decompose unitaries of arbitrary order into binary observables which maintains
certain commutation relations. Such decomposition is different from what Slofstra used in his work \cite{slofstra2017}.
\carl{Our work is heavily based on \cite{slofstra2017}, and we need to make that clearer.}
Intuitively, such decomposition can be seen as the inverse of the Jordan's lemma decomposition.
The third contribution is that we prove self-testing without using anti-commutation relations between Pauli operators, 
which is the core idea in \hf{most of} the previous self-testing results.
\carl{Are we sure about that ("all")?}
Instead, we find a new pair of operators that can generate the ring of matrices over complex numbers.

@@

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
\textbf{Notations}.
We use $[n]$ to denote the set $\{0,1 \dots n-1\}$ and $[n]+1$ for the set $\{1,2 \dots n\}$.
The maximally entangled state of local dimension $d-1$ for some prime $d$ is denoted by
\begin{align}
\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{j = 1}^{d-1} \ket{j}\ket{d-j}.
\end{align}
The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
We denote a Hilbert space by $\calH$. Note that we only work with finite Hilbert spaces in this work.
When there are multiple Hilbert spaces, we label them with subscripts, for example, $\calH_A$ and
$\calH_B$.
The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. In the qubit case, the Pauli operators
are defined by
\begin{align}
	\paulix = \ketbra{0}{1}+\ketbra{1}{0} && \pauliz = \ketbra{0}{0} - \ketbra{1}{1}.
\end{align}

For quantum states and operators on different Hilbert spaces, we use subscripts to label them.
For example, $O_A$ is an operator on Alice's side and $\ket{0}_{B}$ is a state on Bob's side. 
The only exception is for projectors used in a quantum strategy defined below, where the subscript 
is the input and the superscript is the output. For example, $A_x^a$ is Alice's projector for input $x$ and output $a$.
Operators defined by the projectors follow the same convention. For example, $A_x := A_x^0 - A_x^1$.

We use the following notation for the closeness between states.
\begin{align}
	\ket{u} \appd{\epsilon} \ket{v} \iff \norm{\ket{u} - \ket{v}} \leq \epsilon. 
\end{align}
Similarly, for $a,b \in \C$, we have
$a \appd{\epsilon} b \iff \norm{a-b} \leq \epsilon$.

\textbf{Number theory}.
We use some basic number theory in our work. A primitive root of a prime number
$d$ is \hf{the smallest integer} $r$ such that $r \pmod{d}$ has multiplicative order $d-1$
in the multiplicative group of integers modulo $d$, $\Zd$. Equivalently,
$r$ is the generator of $\Zd$.

%We self-test $\ket{\EPR{d-1}}$ by verify that Alice and Bob has operators
%\begin{align}
%	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/r}{k},
%\end{align}
%where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity,
%and $r$ is the primitive root of $d$.  \carl{That sentence is jumping ahead --- you should just stick to
%definitions and notation for now.}
%Through out this paper, any operation on the label of the eigenvector $\ket{k}$ is taken modulo $d$,
%unless otherwise specified, for example, the $k/r$ above.

@@

A quantum strategy of a nonlocal game consists of projective measurements $\{\{A_x^a\}_a\}_x$ on Alice's side, 
$\{\{B_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where a projective measurement $P$ satisfies
the condition that $P^2 = P = P\ct$.  \carl{You need to put explicit labels on the quantum systems used by
Alice and Bob.  (Later on you seem to use ``$A$'' and ``$B$'' to refer to those systems, but those are also
the same letters you use for Alice's and Bob's measurements.  That's confusing.)}
\hf{Addressed in the notation part. --H.F}
Then Alice and Bob's quantum strategy produces the correlation
\begin{align}
	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
where $(A_x^a)^2 = A_x^a = (A_x^a)^\dagger$ and $(B_y^b)^2 = B_y^b = (B_y^b)^\dagger$.
A particular type of nonlocal games that we are interested in is called linear system games, which is defined below.

\begin{definition}[Linear system game]
 Let $Hx = c$ be an $m \times n$ system of linear equations over $\Z_2$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2 = \{0,1\}$ and 
 $c$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = [m]+1$ and replies with $a \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = [n]+1$ and replies with an assignment $b \in \calB = \Z_2$. The winning condition is 
 that Alice's assignment to the variables should satisfy equation $i$ and Alice's $j$-th assignment $a(j)$ should match $b$.
 Formally, the winning condition is 
 \begin{align*}
 	a(j) &= b && \text{(Consistency)} \\
	\sum_{k= 1}^n H(i,k) a(k) &\equiv c(i) \pmod 2. &&\text{(Constraint satisfaction)},
 \end{align*}
 for all $(i,j) \in \calX \times \calY$. 
\end{definition}
The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.  \carl{Make this clear in the definition itself.}
We focus on quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy for the linear system game $(Hx = c)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{c(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement, and
vice versa.  \carl{This is not entirely true.  A ``quantum strategy presented in terms of projective measurement'' allows
Alice to give answers that violate the ``Constraint satisfaction'' condition, while a ``quantum strategy presented 
in terms of binary observables'' does not.}

%It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
%satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
%operator solution in the following sense.  \carl{There's a missing reference here?}
%\begin{definition}[Operator solution of a linear system]
%\label{def:op_sol}
%	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of \hf{finite-dimensional} Hermitian 
%	operators \hf{with finite entries}: $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that \carl{(What does the word ``bounded'' mean here?  It might
%	be best to just state the definition for finite dimensions only.)}
%	\begin{enumerate}
%		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
%		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
%		\item for all $1 \leq i \leq m$,
%		\begin{align*}
%			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
%		\end{align*}
%	\end{enumerate}
%	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
%	solution in which the Hilbert space is finite-dimensional.
%\end{definition}
%Perfect quantum strategies can be extracted from operator solutions and vice versa.
%Another angle to look at the linear system game ($Hx = c$) is a finitely presented group
%over $\Z_2$, which is called the solution group.
%\begin{definition}[Solution group of a linear system game]
%	\label{def:presentation}
%	Let $Hx = c$ be an $m \times n$  linear system. The solution group of this system
%	is the group
%	\begin{align*}
%		\Gamma(H,c) := \ip{
%		x_1,\dots x_n, J: &J^2 = x_i^2 = e \text{ for all }1 \leq i \leq n, \\
%				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
%				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
%				} .
%	\end{align*}
%\end{definition}
%\carl{Don't you also need a commutativity condition for $J$ with $\{ x_i \}$?}
%For concepts about group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
%Combining \cref{def:op_sol} and \cref{def:presentation}, we know that an operator solution associated to $Hx =c$ is 
%a finite-dimensional representation of $\Gamma(H,c)$ that maps $J$ to $-\1$.

\textbf{The weighted CHSH inequality \cite{acin2012}.}
The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
In the CHSH scenario, $\calX = \calY = \{1, 2\}$ and $\calA = \calB = \{0,1\}$.
We define binary observables $A_x := A_x^0 - A_x^1$ and $B_y := B_y^0 - B_y^1$ from Alice and Bob's projectors.
It is easy to see that the binary observables are Hermitian and their only eigenvalues are either $+1$ or $-1$.
The weighted CHSH inequality is given by 
\begin{align}
	\label{eq:chsh_op}
	\ip{\I_\alpha} = \alpha\ip{A_1B_1}+\alpha\ip{A_1B_2} + \ip{A_2B_1} - \ip{A_2B_2}\leq 2\alpha,
\end{align}
where $\ip{A_xB_y} := \bra{\psi} A_x B_y \ket{\psi}$ is the expectation value of of the observables. 
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
the weighted CHSH inequality.
However, If they share entangled state $\ket{\psi}$, the maximal violation is 
\begin{align}
\label{eq:chsh_max}
 \ip{\I_\alpha}_{\max} = 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy to achieve $\ip{\I_\alpha}_{\max}$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
	consists of the joint state $\ket{\EPR{2}}$ and observables $A_1 = \pauliz$, $A_2 = \paulix$,
	$B_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
measurements up to isometry, 
which is a phenomenon referred as a self-test.
We give the definition of a self-test below and the
formal statement of this self-testing property of $\I_\alpha$. in \cref{sec:chsh}.

%Note that we may use the term behaviour and correlation interchangeably.
%The value of a strategy is given by
%\begin{align}
%	\omega(G,p)  = \sum_{a,b,x,y} \pi(x,y) \pr{ab}{xy} V(a,b,x,y).
%\end{align}

%The main contribution of our work is the construction of a correlation, which is the combination of 
%the optimal correlation of a linear system game with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
%and the optimal correlation to violate the weighted CHSH inequality.  \carl{The reader does not 
%know yet what a linear system game is, so this comment is more confusing than helpful.}
%The special property of the correlation is that it can self-test $\ket{\EPR{d-1}}$ for arbitrary $d$ with certain 
%primitive root. 
%In the next part, we introduce the definition of self-testing, the definition of linear system game, 
%and its operator solution, 
%following definitions given in Ref.~\cite{coladan2017, slofstra2017}.

\carl{Before the next definition, you should define what a ``correlation'' is.}
\hf{Mentioned in the nonlocal game part, but not sure how to make it a definition. --HF}
\begin{definition}[Self-testing]
	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
	such that 	
	\begin{align*}
		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
	\end{align*}
\end{definition}
